A Flexible Generator of Constrained Global Optimization Test Problems

### 2018-04-27 2018/LeGo/LeGo.tex
Some corrections

\usepackage[numbers]{natbib}
\usepackage{rotating}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{enumitem}

@@

\begin{abstract}
In the present work, further development of an approach to constructing the test global 
optimization problems with nonlinear constraints is considered. In the generated problems, the 
location of the global minimum is known. The considered generator is featured by an option of 
specifying desired number of constraints and the fraction of feasible domain relative to the 
whole global search domain. In the updated version of the generator, the options of forming the 
problems with a conditional minimum located at the boundary of the feasible domain and of 
specifying the number of constraints active in the minimum points have been added. The 
demonstration of the developed approach is given on the example of a known index method for 
solving the complex multiextremal optimization problems with nonlinear constraints.
\end{abstract}

@@

In the present work, further development of the approach to generating the global optimization 
problems with nonlinear constraints proposed originally in Ref.~\cite{Gergel2017} has been 
conducted.
When generating the test problems, the necessary number of constraints and the desired fraction 
of the feasible domain relative to the whole global search domain can be specified. 
At that, the location of the global minimum is known for the generated problems that simplifies 
evaluating the results of the numerical experiments essentially. 
in addition to the specified options, 
the following functions have been added in the current version of the generator:

@@

For example, one generator for random samples of two-dimensional test functions has been 
described in \cite{Grishagin2015}. 
%This generator produces two-dimensional functions according to the formula
%\begin{equation} \label{VAG}
%\varphi(y)= -
%\left\{\left(\sum^{7}_{i=1}\sum^{7}_{j=1}A_{ij}g_{ij}(y)+B_{ij}h_{ij}(y)\right)^2 + 
%\left(\sum^{7}_{i=1}\sum^{7}_{j=1}C_{ij}g_{ij}(y)+D_{ij}h_{ij}(y)\right)^2\right\}^{1/2},
%\end{equation}
%where $g_{ij}(y)=\sin(i\pi y_1)\sin(j\pi y_2)$, $h_{ij}(y)=\cos(i\pi y_1)\cos(j\pi y_2)$, 
%$y=(y_1,y_2)\in R^2, \; 0 \leq y_1,y_2 \leq 1$, and coefficients $A_{ij}, B_{ij}, C_{ij}, 
%D_{ij}$  are taken uniformly in the interval $[-1,1]$.
Another generator (\textit{GKLS generator}) for the functions of arbitrary dimensionality with 
known properties (the number of local minima, the size of their domains of attraction, the global 
minimizer, etc.) has been proposed in \cite{Gaviano2003}.  Application of this generator for 
studying some unconstrained optimization algorithms has been described in 
\cite{Paulavicius2014,Sergeyev2015}.

The generator GCGen (Global Constrained optimization problem Generator) which allows to 
generate the test global optimization problems with $m$ constraints based on the functions of 
this class has been proposed in Ref.~\cite{Gergel2017}. In the present paper, the rules, which 
allow formulating the constrained global optimization problems have been proposed so that:
\begin{itemize}
	\item one could control the size of feasible domain with respect to the whole domain of 
the parameters' variation;
	\item the global minimizer of the objective function would be known a priori taking into 
account the constraints;
	\item the global minimizer of the objective function without accounting for the 
constraints would be out of the feasible domain.
\end{itemize}

The location of the conditional minimum at the boundary of the feasible domain is an important 
property featuring the applied constrained optimization problems. 
When generating the problems according to the scheme described in Ref.~\cite{Gergel2017}, 
the conditional minimum, in general, will be located inside the feasible domain. Therefore, the 
options of shifting the conditional minimum to the boundary of the feasible domain as well of 
specifying the number of the active constraints in this one have been added in the new version 
of the problem generator.

>>>>

\usepackage[numbers]{natbib}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{enumitem}

@@

\begin{abstract}
In the present work, further development of an approach to constructing the test global 
optimization problems with nonlinear constraints is considered. In the generated problems, the 
location of the global minimum is known. The considered generator is featured by an option of 
specifying desired number of constraints and the fraction of feasible domain relative to the 
whole global search domain. In the updated version of the generator, the options of forming the 
problems with a conditional minimum located at the boundary of the feasible domain and of 
specifying the number of constraints active in the minimizer have been added. The 
demonstration of the developed approach is given on the example of a known index method for 
solving the complex multiextremal optimization problems with non-convex constraints.
\end{abstract}

@@

In the present work, further development of the approach to generating the global optimization 
problems with non-convex constraints proposed originally in \cite{Gergel2017} has been 
conducted.
When generating the test problems, the necessary number of constraints and the desired fraction 
of the feasible domain relative to the whole global search domain can be specified. 
At that, the location of the global minimum is known for the generated problems that essentially simplifies 
evaluating the results of the numerical experiments. 
In addition to the specified options, the following functions have been added in the current version of the generator:

@@

For example, one generator for random samples of two-dimensional test functions has been 
described in \cite{Grishagin2015}. %more refs
Another generator (\textit{GKLS generator}) for the functions of arbitrary dimensionality with 
known properties (the number of local minima, the size of their domains of attraction, the global 
minimizer, etc.) has been proposed in \cite{Gaviano2003}.  Application of this generator for 
studying some unconstrained optimization algorithms has been described in \cite{Paulavicius2014,Sergeyev2015}.

The generator GCGen (Global Constrained optimization problem Generator) which allows to 
generate the test global optimization problems with $m$ constraints based on the functions of 
this class has been proposed in \cite{Gergel2017}. In the present paper, the rules, which 
allow formulating the constrained global optimization problems have been proposed so that:
\begin{itemize}
	\item one could control the size of feasible domain with respect to the whole domain of 
the parameters' variation;
	\item the global minimizer of the objective function would be known a priori taking into 
account the constraints;
	\item the global minimizer of the objective function without accounting for the 
constraints would be out of the feasible domain.
\end{itemize}

The location of the conditional minimum at the boundary of the feasible domain is an important 
property featuring the applied constrained optimization problems. 
When generating the problems according to the scheme described in \cite{Gergel2017}, 
the conditional minimum, in general, will be located inside the feasible domain. Therefore, the 
options of shifting the conditional minimum to the boundary of the feasible domain as well of 
specifying the number of the active constraints in this one have been added in the new version 
of the problem generator.
